Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-27 mr-review.Rmd
more writing

@burgess_robust_2020 introduced the contamination mixture method for robust and efficient MR
analysis with hundreds of SNPs, some of which may be invalid instruments by violating one or 
more of the three core MR assumptions.

@@

@@

@windmeijer_use_2019
@kang_instrumental_2016

>>>>

@burgess_robust_2020 introduced the contamination mixture method for robust and efficient MR
analysis with hundreds of SNPs, some of which may be invalid instruments by violating one or 
more of the three core MR assumptions. Working in the setting of two-sample MR with GWAS data, they begin by considering a collection of candidate SNP instruments, which may contain some invalid SNP instruments. For each candidate SNP instrument, they calculate the Wald ratio estimate of the causal effect. With the collection of Wald ratio estimates, @burgess_robust_2020 reason that the set of valid SNP instruments have Wald ratio estimates that arise from a normal distribution centered on the true causal parameter with variance equal to that of the Wald ratio estimator. The invalid instruments, however, are assumed to follow a normal distribution centered at zero with a variance greater than that of the Wald ratio estimator. They then work with profile log likelihood over a grid of causal parameter values to make inferences.

@@

@foley_mr-clust_2021

@tchetgen_tchetgen_genius_2021 MR-GENIUS

@fang2021evaluating

@sadreev2021navigating

@@
